\thesistitle

### 2019-08-23 sections/results.tex
Better outlining of tables
Commit before I make big changes
Moved some appendix stuff into the results

\begin{table}[H]
\centering
\begin{tabular}{@{}llllll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
 & Same Method & 8,955 & 10.5\% & & \\ \midrule
\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
 & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
 & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
 & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
 & Ancestor & 199 & 0.2\% & & \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
 & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
 & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
 & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
 & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{sec:setuplocation}).
\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Category & Clone instances & \% \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a certain location} % Sander: miss: Amount of clone instances per location category ofzoiets
\label{tab:location}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llllll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{Partial} & Partial Method & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
 & Partial Constructor & 9,981 & 3.37\% & & \\ \midrule
\multirow{5}{*}{Full} & Full Method & 12,990 & 4.38\% & \multirow{5}{*}{13,173}& \multirow{5}{*}{4,44\%} \\ \cmidrule(lr){2-4}
 & Full Interface & 64 & 0.02\% & & \\ \cmidrule(lr){2-4}
 & Full Constructor & 58 & 0.02\% & & \\ \cmidrule(lr){2-4}
 & Full Class & 37 & 0.01\% & & \\ \cmidrule(lr){2-4}
 & Full Enum & 24 & 0.01\% & & \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
 & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
 & Other & 13,324 & 4.49\% & & \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone contents categories}
\label{tab:contents}
\end{table}

\section{Extract Method}
%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique. The second column shows our measurements for the complete systems (just like the former experiments). The third column shows our measurements when restricting our search to method bodies. % Sander: waarom willen we dat weten?
The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
% Sander: die laatste zin snap ik niet
\begin{table}[H]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\% (All)}} & \textit{\textbf{Method Body}} & \textit{\textbf{\% (Method Body)}} \\ \midrule
Can Be Extracted & 24,157 & 28.2\% & 26,109 & 50.4\% \\
Is Not A Partial Method & 21,625 & 25.3\% & 0 & 0.0\% \\
Top-level AST-Node is not a Statement & 19,887 & 23.2\% & 4,607 & 8.9\% \\
Spans Part of a Block & 12,964 & 15.2\% & 13,460 & 26.1\% \\
Multiple Return Values & 5,622 & 6.6\% & 6,131 & 11.9\% \\
Complex Control Flow & 1,106 & 1.3\% & 1,216 & 2.4\% \\
Overlap In Clone Class & 147 & 0.2\% & 147 & 0.3\% \\
Not In Class Or Interface & 70 & 0.1\% & 93 & 0.2\% \\
\bottomrule
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}

\section{Refactoring}
%I think the ultimate goal with this thesis is to do experiments with different clone thresholds. Which thresholds give clones that we should refactor? For this, we will measure the maintainability of the refactored source code over different thresholds. These thresholds range from minimum clone size, variability, and gap size.
In our corpus, CloneRefactor has refactored 12,710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}). Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) % Sander: Ref geeft ???
influence the maintainability of the resulting codebase after refactoring. In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.

@@

\subsection{Relation}
Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability. We mark rows based on less than 100 refactorings red, as their result does not have statistical significance.

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{Maintainability Score}} & \textit{\textbf{Number of Refactorings}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{0.23} & \textbf{2,202} \\ \midrule
\hspace{10pt} Superclass & 0.42 & 229 \\
\hspace{10pt} Sibling & 0.23 & 1,722 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Same Hierarchy & 0.10 & 87 \\
\hspace{10pt} First Cousin & 0.02 & 144 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Ancestor & -0.03 & 20 \\ \midrule
\textbf{Common Interface} & \textbf{-0.02} & \textbf{1,044} \\ \midrule
\hspace{10pt} Same Indirect Interface & -0.01 & 487 \\
\hspace{10pt} Same Direct Interface & -0.02 & 557 \\ \midrule
\textbf{Common Class} & \textbf{-0.02} & \textbf{7,239}\\ \midrule
\hspace{10pt} Same Class & 0.04  & 4,874 \\
\hspace{10pt} Same Method & -0.15 & 2,365  \\ \midrule
\textbf{Unrelated} & \textbf{-0.15} & \textbf{2,198}\\ \midrule
\hspace{10pt} No Direct Superclass & -0.06 & 811 \\
\hspace{10pt} External Superclass & -0.17 & 697  \\
\hspace{10pt} External Ancestor & -0.21 & 586  \\
\hspace{10pt} No Indirect Superclass & -0.30 & 104  \\ \midrule
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

\subsection{Return Value}
Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system (categories are explained in Section~\ref{sec:refreturn}).

\begin{table}[H]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
Return & 0.19 & 1,571 \\
Declare & 0.15 & 5,177 \\
\rowcolor[HTML]{FFCCC9}
Assign & 0.12 & 14 \\
Void & -0.18 & 5,921 \\
\bottomrule
\end{tabular}
\caption{Maintainability scores for different methods of handling returned data from the call to the extracted method.}
\label{tab:return}
\end{table}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{@{}llrrrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
 & Same Method & 8,955 & 10.5\% & & \\ \midrule
\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
 & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
 & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
 & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
 & Ancestor & 199 & 0.2\% & & \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
 & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
 & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
 & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
 & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{sec:setuplocation}).
\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
Category & Clone instances & \% \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a certain location} % Sander: miss: Amount of clone instances per location category ofzoiets
\label{tab:location}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llrrrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{Partial} & Partial Method & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
 & Partial Constructor & 9,981 & 3.37\% & & \\ \midrule
\multirow{5}{*}{Full} & Full Method & 12,990 & 4.38\% & \multirow{5}{*}{13,173}& \multirow{5}{*}{4,44\%} \\ \cmidrule(lr){2-4}
 & Full Interface & 64 & 0.02\% & & \\ \cmidrule(lr){2-4}
 & Full Constructor & 58 & 0.02\% & & \\ \cmidrule(lr){2-4}
 & Full Class & 37 & 0.01\% & & \\ \cmidrule(lr){2-4}
 & Full Enum & 24 & 0.01\% & & \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
 & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
 & Other & 13,324 & 4.49\% & & \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone contents categories}
\label{tab:contents}
\end{table}

\section{Extract Method}
%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique. The second column shows our measurements for the complete systems (just like the former experiments). The third column shows our measurements when restricting our search to method bodies. % Sander: waarom willen we dat weten?
The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
% Sander: die laatste zin snap ik niet
\begin{table}[H]
\centering
\begin{tabular}{@{}lrrrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\% (All)}} & \textit{\textbf{Method Body}} & \textit{\textbf{\% (Method Body)}} \\ \midrule
Can Be Extracted & 24,157 & 28.2\% & 26,109 & 50.4\% \\
Is Not A Partial Method & 21,625 & 25.3\% & 0 & 0.0\% \\
Top-level AST-Node is not a Statement & 19,887 & 23.2\% & 4,607 & 8.9\% \\
Spans Part of a Block & 12,964 & 15.2\% & 13,460 & 26.1\% \\
Multiple Return Values & 5,622 & 6.6\% & 6,131 & 11.9\% \\
Complex Control Flow & 1,106 & 1.3\% & 1,216 & 2.4\% \\
Overlap In Clone Class & 147 & 0.2\% & 147 & 0.3\% \\
Not In Class Or Interface & 70 & 0.1\% & 93 & 0.2\% \\
\bottomrule
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}

\section{Refactoring} \label{sec:refactoringexperiments}
%I think the ultimate goal with this thesis is to do experiments with different clone thresholds. Which thresholds give clones that we should refactor? For this, we will measure the maintainability of the refactored source code over different thresholds. These thresholds range from minimum clone size, variability, and gap size.
In our corpus, CloneRefactor has refactored 12,710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}). Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) % Sander: Ref geeft ???
influence the maintainability of the resulting codebase after refactoring. In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring. We use the following keywords as headers of the columns of our tables:
\begin{itemize}
  \item \textbf{Complexity}: The average delta complexity for all refactored clone classes in the specified category.
  \item \textbf{Parameters}: The average delta number of parameters for all refactored clone classes in the specified category.
  \item \textbf{Volume}: The average delta number of tokens for all refactored clone classes in the specified category.
  \item \textbf{Duplication}: The average delta number of duplicate tokens for all refactored clone classes in the specified category.
  \item \textbf{\#}: The number of times the specified category is refactored (and thus the number of datapoints we have for this category).
  \item \textbf{Score}: The average delta maintainability score (see Section~\ref{sec:metricformula} for the formula by which this score is calculated) for all refactored clone classes in the specified category.
\end{itemize}
In this context, the \textit{delta} denotes the change in this metric between the before- and after-refactoring snapshot of the system, for each separate clone class that was refactored.

@@

\subsection{Relation}
Table~\ref{tab:full-relation} shows our data regarding how different relations influence maintainability. We mark rows based on less than 100 refactorings red, as their result does not have statistical significance. The \textbf{Relation} column refers to the relations introduced in Section~\ref{sec:setuprelation}. Relations are mutually exclusive so all percentages add up to 100\%.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
}
\caption{Average metric values for refactorings of clone classes with the specified relations}
\label{tab:full-relation}
\end{table}

\subsection{Return Category}
Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system. The \textbf{Return Category} column refers to the categories introduced in Section~\ref{sec:refreturn}.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Interface Size}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}%
}
\caption{Average metric values for refactorings of clone classes with the specified return category}
\label{tab:full-return}
\end{table}
